|

### 2023-06-06 replication_materials/dcpo_demsupport.Rmd
add osf links

## Loading replication data
load(here("data", "correct_cls_ajps.rda")) # https://osf.io/52u7n/download
load(here("data", "correct_cls_apsr.rda")) # https://osf.io/cws59/download
load(here("data", "expcor_cls_ajps.rda"))  # https://osf.io/cgxjd/download
load(here("data", "expcor_cls_apsr.rda"))  # https://osf.io/uka5g/download
exp_claassen_input <- rio::import(here("data", "exp_claassen_input.rds")) # https://osf.io/fcyn3/download

## Preloading chunk-produced results to speed up the compiling
## One can find how they were created by locating the corresponding chunks

result_clsAPSR <-
    readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
result_clsAJPS <-
    readRDS(here("output", "estimates_clsMeanAJPS.RDS"))

mocresult_correctAJPS <-
    readRDS(here("output", "estimates_moc_correctAJPS.RDS"))
mocresult_expAJPS <-
    readRDS(here("output", "estimates_moc_expcorAJPS.RDS"))
mocresult_correctAPSR <-
    readRDS(here("output", "estimates_moc_correctAPSR.RDS"))
mocresult_expAPSR <-
    readRDS(here("output", "estimates_moc_expcorAPSR.RDS"))
mocdcpo_APSR <- readRDS(here("output", "estimates_moc_dcpoAPSR.RDS"))
mocresult_dcpoAJPS <-
    readRDS(here("output", "estimates_moc_dcpoAJPS.RDS"))
```

@@

file.copy(
        c(
            "estimates_moc_dcpoAPSR.RDS",
            "estimates_moc_dcpoAJPS.RDS"
        ),
        "output"
    )

## Replication data
load(here("data", "dcpo_ajps.rda"))  # https://osf.io/xw9fr/download
load(here("data", "dcpo_apsr.rda"))  # https://osf.io/j7kn3/download

## Preloading chunk-produced results to speed up the compiling
## One can find how they were created by locating the corresponding chunks

mocdcpo_APSR <- readRDS(here("output", "estimates_moc_dcpoAPSR.RDS"))
mocresult_dcpoAJPS <-
    readRDS(here("output", "estimates_moc_dcpoAJPS.RDS"))
```

>>>>

## Loading replication data
# Download from osf if files not present 
# (can also be generated by compiling /data_replication/data_replication.Rmd)
if (!file.exists(here("data",
                      "correct_cls_ajps.rda"))) { 
    osf_retrieve_file("5xyvt") %>% 
        osf_download(here("data"))
}
if (!file.exists(here("data",
                      "correct_cls_apsr.rda"))) { 
    osf_retrieve_file("8xgm4") %>% 
        osf_download(here("data"))
}
if (!file.exists(here("data",
                      "expcor_cls_ajps.rda"))) { 
    osf_retrieve_file("rj9g5") %>% 
        osf_download(here("data"))
}
if (!file.exists(here("data",
                      "expcor_cls_apsr.rda"))) { 
    osf_retrieve_file("bxt7m") %>% 
        osf_download(here("data"))
}
if (!file.exists(here("data",
                      "exp_claassen_input.rds"))) { 
    osf_retrieve_file("rfamx") %>% 
        osf_download(here("data"))
}
if (!file.exists(here("data",
                      "dcpo_ajps.rda"))) { 
    osf_retrieve_file("sbp5a") %>% 
        osf_download(here("data"))
}
if (!file.exists(here("data",
                      "dcpo_apsr.rda"))) { 
    osf_retrieve_file("9yh5z") %>% 
        osf_download(here("data"))
}

## Loading replication data
load(here("data", "correct_cls_ajps.rda"))
load(here("data", "correct_cls_apsr.rda"))
load(here("data", "expcor_cls_ajps.rda")) 
load(here("data", "expcor_cls_apsr.rda")) 
exp_claassen_input <- rio::import(here("data", "exp_claassen_input.rds")) 
load(here("data", "dcpo_ajps.rda"))
load(here("data", "dcpo_apsr.rda"))

## Preloading chunk-produced results to speed up the document compiling
# Download from osf if files not present 
# (can also be generated by compiling the appropriate eval=FALSE chunks below)
if (!file.exists(here("output",
                      "estimates_clsMeanAJPS.RDS"))) { 
    osf_retrieve_file("s36h2") %>% 
        osf_download(here("output"))
}
if (!file.exists(here("output",
                      "estimates_clsMeanAPSR.RDS"))) { 
    osf_retrieve_file("cuj63") %>% 
        osf_download(here("output"))
}
if (!file.exists(here("output",
                      "estimates_moc_correctAJPS.RDS"))) { 
    osf_retrieve_file("nbt4j") %>% 
        osf_download(here("output"))
}
if (!file.exists(here("output",
                      "estimates_moc_expcorAJPS.RDS"))) { 
    osf_retrieve_file("hd874") %>% 
        osf_download(here("output"))
}
if (!file.exists(here("output",
                      "estimates_moc_correctAPSR.RDS"))) { 
    osf_retrieve_file("fv3qz") %>% 
        osf_download(here("output"))
}
if (!file.exists(here("output",
                      "estimates_moc_expcorAPSR.RDS"))) { 
    osf_retrieve_file("td5nr") %>% 
        osf_download(here("output"))
}
if (!file.exists(here("output",
                      "estimates_moc_dcpoAJPS.RDS"))) { 
    osf_retrieve_file("8avpt") %>% 
        osf_download(here("output"))
}
if (!file.exists(here("output",
                      "estimates_moc_dcpoAPSR.RDS"))) { 
    osf_retrieve_file("e2ys3") %>% 
        osf_download(here("output"))
}

result_clsAJPS <-
    readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
result_clsAPSR <-
    readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
mocresult_correctAJPS <-
    readRDS(here("output", "estimates_moc_correctAJPS.RDS"))
mocresult_expAJPS <-
    readRDS(here("output", "estimates_moc_expcorAJPS.RDS"))
mocresult_correctAPSR <-
    readRDS(here("output", "estimates_moc_correctAPSR.RDS"))
mocresult_expAPSR <-
    readRDS(here("output", "estimates_moc_expcorAPSR.RDS"))
mocresult_dcpoAJPS <-
    readRDS(here("output", "estimates_moc_dcpoAJPS.RDS"))
mocdcpo_APSR <- readRDS(here("output", "estimates_moc_dcpoAPSR.RDS"))

@@

file.copy(
        c(
            "estimates_moc_dcpoAPSR.RDS",
            "estimates_moc_dcpoAJPS.RDS"
        ),
        "output"
    )
```
